Supporting Information

### 2018-04-02 SupportingInformation.Rmd
minor editing changes after shya added the plots of the nonparam stats versus distance for the aphid datasets

<!--checkpoint package-->
```{r checkpoint_chunk, echo=F, warning=F, message=F, results="hide"}
library(checkpoint)
if (!dir.exists("./.checkpoint/")){
  dir.create("./.checkpoint/")
}
checkpoint("2018-03-29",checkpointLocation = "./")
```

@@

Plotting Spearman or Kendall correlation between aphid abundance time series for pairs of locations as a function of great circle distance
between the locations (Figure \ref{fig_aphid_count} A,B) showed the typical decline of correlation with 
distance between sampling locations that has been seen for numerous other datasets in earlier work. Plotting 
$\cor_l$, $\cor_u$, $\Ps_l$, $\Ps_u$, $\Dsq_u$ and  $\Dsq_l$ against distance between pairs of  
locations shows these quantities also decline with distance (Figure \ref{fig_aphid_count} C-H).
<!--DAN add reference and revisit the text here once Shya add these panels-->
Plotting $\cor_l - \cor_u$, $\Ps_l - \Ps_u$, and $\Dsq_u - \Dsq_l$ versus distance (Figure \ref{fig_aphid_count} I-K)
did not show a decline with distance, but did illustrate visually the statistical
result of Table \ref{tab_count_resamp} that averages of these quantities across all pairs of sampling locations
were significantly greater than zero, demonstrating asymmetry of tail dependence.
Code for these analyses is in [`NonParamStat.R`](https://github.com/sghosh89/BIVAN/blob/master/NonParamStat.R) in 
the [`BIVAN`](https://github.com/sghosh89/BIVAN) package.

<!--Shya, can you please add panels for corl, coru, Pl, Pu, D2l, D2u vs. distance, following the Spearman and Kendall
panels? I think it will be the first time anyone has shown these, so we should show the decline with distance
holds for these as well. That means you'll have 6 new panels, for a total of 11 panels. So it'll be a big figure, 
possibly taking up a whole page, or most of one. Similar changes, please,
to the analogous figs for the aphid ff and ceratium furca data.-->
\begin{figure}[!h]
\textbf{ \hspace{2.6 cm} (A) \hspace{3.6 cm} (B) \hspace{3.8 cm} (C) \hspace{3.8 cm} (D)} \\
\begin{center}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_count/Sp_10_Spearman_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_count/Sp_10_Kendall_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_count/Sp_10_Corl_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_count/Sp_10_Coru_vs_D.pdf}\\
\end{center}
\textbf{ \hspace{2.6 cm} (E) \hspace{3.6 cm} (F) \hspace{3.8 cm} (G) \hspace{3.8 cm} (H)} \\
\begin{center}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_count/Sp_10_Pl_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_count/Sp_10_Pu_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_count/Sp_10_D2u_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_count/Sp_10_D2l_vs_D.pdf}\\
\end{center}
\textbf{ \hspace{4.8 cm} (I) \hspace{3.8 cm} (J) \hspace{4 cm} (K) } \\
\begin{center}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_count/Sp_10_Corl-Coru_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_count/Sp_10_Pl-Pu_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_count/Sp_10_D2u-D2l_vs_D.pdf}
\caption{Non-parametric tail statistics results for green spruce aphid abundance data plotted against geographical distance ($D$) between two sampling locations. (A) Spearman correlation vs. $D$; (B) Kendall correlation vs. $D$; (C) $\cor_l$ vs. $D$; (D) $\cor_u$ vs. $D$; (E) $\Ps_l$ vs. $D$; (F) $\Ps_u$ vs. $D$; (G) $\Dsq_u$ vs. $D$; 
(H) $\Dsq_l$ vs. $D$; 
(I) $\cor_l-\cor_u$ vs. $D$, (J) $\Ps_l-\Ps_u$ vs. $D$, (K) $\Dsq_u-\Dsq_l$ vs. $D$ plotted for all 
pairs of locations. \label{fig_aphid_count}}
\end{center}
\end{figure}

@@

Plotting Spearman or Kendall correlations between first flight time series for pairs of locations as a function of great circle distance between the locations (Figure \ref{fig_aphid_ff} A, B) showed the typical (though slight, in this case) decline of correlation with increasing distance. Plotting $\cor_l$, $\cor_u$, $\Ps_l$, $\Ps_u$, $\Dsq_u$, and $\Dsq_l$ against distances between pairs of locations shows these quantities also decline with distance (Figure \ref{fig_aphid_ff} C-H).
<!--DAN: make sure this is true when you see the plots again-->
Plotting $\cor_l - \cor_u$, $\Ps_l - \Ps_u$, and $\Dsq_u - \Dsq_l$ against distance (Figure \ref{fig_aphid_ff} I-K) did not show a decline with distance, but did demonstrate visually the statistical result of Table \ref{tab_ff_resamp} that averages of these quantities across all pairs of sampling locations were significantly less than zero, showing asymmetry of tail dependence.

<!--Shya, pls add 6 new panels as described in my comment near the analogous figure for aphid count-->
\begin{figure}[!h]
\textbf{ \hspace{2.6 cm} (A) \hspace{3.6 cm} (B) \hspace{3.8 cm} (C) \hspace{3.8 cm} (D)} \\
\begin{center}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_ff/Sp_11_Spearman_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_ff/Sp_11_Kendall_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_ff/Sp_11_Corl_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_ff/Sp_11_Coru_vs_D.pdf}\\
\end{center}
\textbf{ \hspace{2.6 cm} (E) \hspace{3.6 cm} (F) \hspace{3.8 cm} (G) \hspace{3.8 cm} (H)} \\
\begin{center}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_ff/Sp_11_Pl_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_ff/Sp_11_Pu_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_ff/Sp_11_D2u_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_ff/Sp_11_D2l_vs_D.pdf}\\
\end{center}
\textbf{ \hspace{4.8 cm} (I) \hspace{3.8 cm} (J) \hspace{4 cm} (K) } \\
\begin{center}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_ff/Sp_11_Corl-Coru_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_ff/Sp_11_Pl-Pu_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_ff/Sp_11_D2u-D2l_vs_D.pdf}
\caption{Non-parametric tail statistics results for leaf-curling plum aphid's first flight date data plotted against geographical distance $(D)$ between two sampling locations. (A) Spearman correlation vs. $D$, (B) Kendall correlation vs. $D$, (C) $\cor_l$ vs. $D$, (D) $\cor_u$ vs. $D$; (E) $\Ps_l$ vs. $D$; (F) $\Ps_u$ vs. $D$; (G) $\Dsq_u$ vs. $D$; (H) $\Dsq_l$ vs. $D$; (I) $\cor_l-\cor_u$ vs. $D$; (J) $\Ps_l-\Ps_u$ vs. $D$; (K) $\Dsq_u-\Dsq_l$ vs. $D$ plotted for all pairs of locations. \label{fig_aphid_ff}}
\end{center}
\end{figure}

@@

<!--DAN: effectively stopped here 2018 04 01 10pm-->

>>>>

<!--checkpoint package-->
```{r checkpoint_chunk, echo=F, warning=F, message=F, results="hide"}
library(checkpoint)
library(captioner)
if (!dir.exists("./.checkpoint/")){
  dir.create("./.checkpoint/")
}
checkpoint("2018-03-29",checkpointLocation = "./")
```

@@

Plotting Spearman or Kendall correlation between aphid abundance time series for pairs of locations as a function of great circle distance
between the locations (Figure \ref{fig_aphid_count} A,B) showed the typical decline of correlation with 
distance between sampling locations that has been seen for numerous other datasets in earlier work. Plotting 
$\cor_l$, $\cor_u$, $\Ps_l$, and $\Ps_u$  against distance between pairs of 
locations shows these quantities also decline with distance (Figure \ref{fig_aphid_count} C-F). Plotting $\Dsq_u$ and  $\Dsq_l$ against distance between pairs of locations shows
these quantities increase with distance (as expected, given the opposite interpretation 
these
two statistics have compared to $\cor_u$, $\Ps_u$ and $\cor_l$, $\Ps_l$, respectively).
Plotting $\cor_l - \cor_u$, $\Ps_l - \Ps_u$, and $\Dsq_u - \Dsq_l$ versus distance (Figure \ref{fig_aphid_count} I-K)
did not show a decline with distance, but did illustrate visually the statistical
result of Table \ref{tab_count_resamp} that averages of these quantities across all pairs of sampling locations
were significantly greater than zero, demonstrating asymmetry of tail dependence.
Code for these analyses is in [`NonParamStat.R`](https://github.com/sghosh89/BIVAN/blob/master/NonParamStat.R) in 
the [`BIVAN`](https://github.com/sghosh89/BIVAN) package.

\begin{figure}[!h]
\textbf{ \hspace{2.6 cm} (A) \hspace{3.6 cm} (B) \hspace{3.8 cm} (C) \hspace{3.8 cm} (D)} \\
\begin{center}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_count/Sp_10_Spearman_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_count/Sp_10_Kendall_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_count/Sp_10_Corl_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_count/Sp_10_Coru_vs_D.pdf}\\
\end{center}
\textbf{ \hspace{2.6 cm} (E) \hspace{3.6 cm} (F) \hspace{3.8 cm} (G) \hspace{3.8 cm} (H)} \\
\begin{center}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_count/Sp_10_Pl_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_count/Sp_10_Pu_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_count/Sp_10_D2u_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_count/Sp_10_D2l_vs_D.pdf}\\
\end{center}
\textbf{ \hspace{4.8 cm} (I) \hspace{3.8 cm} (J) \hspace{4 cm} (K) } \\
\begin{center}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_count/Sp_10_Corl-Coru_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_count/Sp_10_Pl-Pu_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_count/Sp_10_D2u-D2l_vs_D.pdf}
\caption{Non-parametric tail statistics results for green spruce aphid abundance data plotted against geographical distance ($D$) between two sampling locations. (A) Spearman correlation vs. $D$; (B) Kendall correlation vs. $D$; (C) $\cor_l$ vs. $D$; (D) $\cor_u$ vs. $D$; (E) $\Ps_l$ vs. $D$; (F) $\Ps_u$ vs. $D$; (G) $\Dsq_u$ vs. $D$; 
(H) $\Dsq_l$ vs. $D$; 
(I) $\cor_l-\cor_u$ vs. $D$, (J) $\Ps_l-\Ps_u$ vs. $D$, (K) $\Dsq_u-\Dsq_l$ vs. $D$ plotted for all 
pairs of locations. \label{fig_aphid_count}}
\end{center}
\end{figure}

@@

Plotting Spearman or Kendall correlations between first flight time series for pairs of locations as a function of great circle distance between the locations (Figure \ref{fig_aphid_ff} A, B) showed the typical (though slight, in this case) decline of correlation with increasing distance. Plotting $\cor_l$, $\cor_u$, $\Ps_l$, and $\Ps_u$ against distances between pairs of locations shows these quantities also appear in most cases to decline slightly with distance (Figure \ref{fig_aphid_ff} C-F).
$\Dsq_u$ and $\Dsq_l$ appear to slightly increase with distance, as expected given their
opposite meaning (Figure \ref{fig_aphid_ff} G-H). 
Plotting $\cor_l - \cor_u$, $\Ps_l - \Ps_u$, and $\Dsq_u - \Dsq_l$ against distance (Figure \ref{fig_aphid_ff} I-K) did not show a decline with distance, but did demonstrate visually the statistical result of Table \ref{tab_ff_resamp} that averages of these quantities across all pairs of sampling locations were significantly less than zero, showing asymmetry of tail dependence.

\begin{figure}[!h]
\textbf{ \hspace{2.6 cm} (A) \hspace{3.6 cm} (B) \hspace{3.8 cm} (C) \hspace{3.8 cm} (D)} \\
\begin{center}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_ff/Sp_11_Spearman_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_ff/Sp_11_Kendall_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_ff/Sp_11_Corl_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_ff/Sp_11_Coru_vs_D.pdf}\\
\end{center}
\textbf{ \hspace{2.6 cm} (E) \hspace{3.6 cm} (F) \hspace{3.8 cm} (G) \hspace{3.8 cm} (H)} \\
\begin{center}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_ff/Sp_11_Pl_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_ff/Sp_11_Pu_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_ff/Sp_11_D2u_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_ff/Sp_11_D2l_vs_D.pdf}\\
\end{center}
\textbf{ \hspace{4.8 cm} (I) \hspace{3.8 cm} (J) \hspace{4 cm} (K) } \\
\begin{center}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_ff/Sp_11_Corl-Coru_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_ff/Sp_11_Pl-Pu_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_aphid_ff/Sp_11_D2u-D2l_vs_D.pdf}
\caption{Non-parametric tail statistics results for leaf-curling plum aphid's first flight date data plotted against geographical distance $(D)$ between two sampling locations. (A) Spearman correlation vs. $D$, (B) Kendall correlation vs. $D$, (C) $\cor_l$ vs. $D$, (D) $\cor_u$ vs. $D$; (E) $\Ps_l$ vs. $D$; (F) $\Ps_u$ vs. $D$; (G) $\Dsq_u$ vs. $D$; (H) $\Dsq_l$ vs. $D$; (I) $\cor_l-\cor_u$ vs. $D$; (J) $\Ps_l-\Ps_u$ vs. $D$; (K) $\Dsq_u-\Dsq_l$ vs. $D$ plotted for all pairs of locations. \label{fig_aphid_ff}}
\end{center}
\end{figure}

@@
